Adaption of the Chumbley Score to matching of bullet striation marks

### 2017-10-29 doc/paper.Rmd
introduction and other changes, results from chumbley and hadler included.
some information on profiles and how they are being used in the chumbley algorithm _.

\hh{XXX the process you describe below is the cross-correlation of two series $x(t)$ and $y(t)$. }

@@

>>>>

\hh{XXX the process you describe below is the cross-correlation of two series $x(t)$ and $y(t)$.}

@@

### Profiles

The profiles are cross-sectional values of the the bullet striation mark which are chosen at an optimum height (x as used by \citet{aoas}). This x or height is not a randomly chosen level. The rationale behind the choice has been explained by \citet{aoas}. A region is first chosen where the cross-correlation seems to change very less and in this region an optimum height is chosen. The profiles generally resemble a curve which is more or less similar to a quadratic curve (a quadratic fit to the raw data values of the profile is not an exact fit but it does show a similar trend). Profiles are the set of raw values representing the striation marks, and signatures are generated from these by removal of the inherent curvature and applying some smoothing (the signatures generated by \citet{aoas} use a loess function for smoothing).

Coming back to the database of Hamby 44 and Hamby 252 datasets, the run_id = 3 was used when applying the chumbley algorithm on the signatures. The run_id not only defines the level of smoothing but also signifies the chosen height at which the profiles were selected initially.
Another important aspect is the range of horizontal values (which is referred to as the y values in \citet{aoas}) in the signatures. Thes have already been pre-processed in the database to not include any grooves.

Therefore for the sake of comparison the run_id = 3 is still chosen so as to ensure that the horizontal values remain the same as that of the signatures. This also gives us profiles with the grooves removed.

The idea therefore is to first use these raw values of the profile directly in the chumbley algorithm, and see how the algorithm performs for different coarseness values (smoothing parameter as referred in the function LOWESS used in the chumbley algorithm).
